TODO: A Survey of StarCraft AI Techniques

### 2011-10-09 survey.tex
Started writing a section on overall architecture of bots (still WIP)

\usepackage{cite}

@@

@@

%\begin{figure}[!t]
%\centering
%\includegraphics[width=4cm]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

>>>>

\usepackage{cite,color,graphicx}

@@

{\color{red} Here we can use Buro's 2003 paper as a starting point. Much has changed since, so we should update, and put his predictions in perspective}

@@

\section{AI Architectures for RTS AI}\label{sec:architecture}

{\color{red}[SANTI: This section is WIP, so, don't read it yet :)]}

Playing an RTS game involves dealing with all the problems described above. A few approaches, like CAT \cite{aha2005cat}, Darmok \cite{ontanon2010darmok} or XXX \cite{some-rl-system} ({\color{red}Which was that system by Stuart Russell that played Warcraft?}) try to deal with the problem in a monolithic manner, by using a single AI technique. This resembles approaches to solve other games, such as Chess or Go, where a single game-tree search approach is enough to play the game at human level. However, none of those systems aims at achieving near human performance. In order to achieve human-level performance, RTS AI designers use a lot of domain knowledge in order to divide the task of playing the game into a collection of sub-problems, which can be dealt-with using individual AI techniques (as discussed in the previous section). Thus, an integration architecture is required to put together all of those techniques into a single coherent system, which is the focus of this section.

...

\begin{figure}[ta]
%    \centering
    \includegraphics[width=\columnwidth]{figures/figure-bot-architectures.pdf}
    \caption{General architecture of 5 Starcraft AI bots. {\color{red} (This figure is unreadable as of now, but we'll figure out a way to better present this info)}}
    \label{fig:bot-architecture}
\end{figure}

{\color{red} Present some representative examples (Figure \ref{fig:bot-architecture}), which have slightly different architectures. I could mention THANATOS as something different using learning, and Darmok as a monolithic architecture that aims at learning how to play the game, without hoping to play at human level.}

{\color{red} Then, draw some general conclusions: 
\begin{itemize}
\item two types of aggregation, hierarchical, and decentralized (bidding?). Hierarchical is multiscale, with actions at different levels of abstraction.
\item high level strategy is hard-coded (unlike in games like Chess or Go): different expressivity of the high-level strategy of the different systems, compare them. It's like a very high level programming language for RTS bots.
\end{itemize}}
